---
title: ""
author: "Jana B. Jarecki"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    keep_tex: yes
documentclass: "apa6"
classoption:
  a4paper,
  man,
  floatsintext
header-includes:
  \usepackage{natbib}
  \usepackage{threeparttable}
  \usepackage{booktabs}
  \shorttitle{test}
  \usepackage{setspace}
  \AtBeginEnvironment{tabular}{\singlespacing}
  \usepackage{times}
  \usepackage{changes}
  \definechangesauthor[name={JJ}, color=orange]{jj}
  \usepackage{upgreek}
  \AtBeginDocument{\let\maketitle\relax}
---

```{r setupknitr, include=0, cache=0}
  source("setup_knitr.R")
```

```{r setupR, include=0, cache=0}
  source("./code/setup_fig.R")
  options(papaja.na_string = "--")
  source("./code/4-evaluations-by-prior.R", chdir = TRUE)
```

\added[id=jj]{Figure \ref{fig:fig6}a shows that, descriptively, among the Bayesian participants, those with zero-outcome priors only slightly increased their evaluations of p-bets, those with gain priors slightly decreased their evaluations of \$-bets, and RF-type participants remained relatively stable across sample sizes, as predicted. However, statistical analyses by means of a Bayesian mixed-effects model}\footnote{Regressing the (normalized, within-person z-standardized) evaluations on the predictors sample size category (coded as 1,2,3,4), gamble type, and learner class (BVU-gain-prior, BVU-loss-prior, RF) and interactions of the predictors, with a by-participant random intercept; categorical predictors were effects-coded to facilitate interpretation of interactions.} \added[id=jj]{revealed that the data failed to strongly support a model with sample size as predictor ($M_0$) over a model without sample size $BF\textsubscript{01} `r BF_value_prior`$.
}

```{r, echo=0, cache=0, fig.height = 5, fig.width = 4, fig.pos = "H"}
  knitr::read_chunk("./code/fig6.R")
```

```{r fig6, cache=FALSE, fig.cap = "Mean evaluations by gamble type and best-fitting cognitive model and prior beliefs of the BVU model. \\textit{BVU}$=$Bayesian value updating model, \\textit{RF}$=$ Relative frequency model. Error bars indicate standard errors. Sample size categories see Table \\ref{table:Lotteries}. Evaluations are scaled to 0-1 and z-standardized at the individual level."}
```

\textit{Predictions about confidence.}
\added[id=jj]{Regarding uncertainty about beliefs, the Bayesian model predicts that the uncertainty about beliefs reduces with more evidence. Thus in Bayesian learners, confidence should increase with growing sample size. The relative frequency model makes no predictions about confidence. To test this, we classified participants into Bayesian and relative-frequency learners based on the best-fitting model. Mean confidence ratings of Bayesian-type learners, z-standardized within participants, increased only slightly from the extra small sample size ($`r d[samplesizecat == "xs" & winner == "bvu", paste_msd(conf_scaled, label = T)]`$), to the small sample size ($`r d[samplesizecat == "s" & winner == "bvu", paste_msd(conf_scaled, label = T)]`$), medium sample size ($`r d[samplesizecat == "m" & winner == "bvu", paste_msd(conf_scaled, label = T)]`$), and large sample size ($`r d[samplesizecat == "l" & winner == "bvu", paste_msd(conf_scaled, label = T)]`$, Figure \ref{fig:fig6}b), but statistical analyses showed that a linear regression model\footnote{Regressing the (within-person z-standardized) confidence ratings on the predictors sample size category (coded as 1,2,3,4), gamble type, and winning model (BVU, RF), and interactions of the predictors, with a by-participant random intercept; categorical predictors were effects-coded to facilitate interpretation of interactions.} ($M_0$) that includes the sample size as predictor fitted the data worse than an intercept-only model ($BF_{01}`r BF_conf_prior`$).}
